Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
changes to the table

\begin{table}[!ht]
\caption{
\bf{Notation and Parameters - Part 2}}
\begin{tabular}{|c|l|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
	\hline
    $L$ & number of field basis functions & 81 & \\
   	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
   	$\mathbf{x}_t$ & state vector at time $t$ & & \\
   	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
   	$\theta$ & vector of connectivity kernel parameters & & \\
   	$\Gamma$ & inner product of field basis functions & &\\
   	$q()$ & state function & &\\
   	$Q()$ & state function & &\\
	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
   	$\mathbf{e}_t$ & state disturbance & &\\
	$\Sigma_e$ &state disturbance covariance matrix& &\\
	$\mathbf{\varepsilon}_t$ & observation noise & &\\
	$\Sigma_{\varepsilon}$ &observation noise covariance matrix& &\\
   	$\mathbf{C}$ & observation matrix& & \\
	$c_{ij}$& elements of observation matrix & & \\
	\hline
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}} \\
	\hline
    $V(\nu)$ & Spectrum of the dynamic field & &\\
	$\nu$ & Spatial frequency & &\\
	$\nu_c$ & Spatial cut-off frequency & &\\
	$\Delta_y$ & Distance between adjacent sensors & &\\
	$\rho$ & Over-sampling parameter & &\\
	$\Delta_{\phi}$ & Distance between field basis functions & &\\
	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function & &\\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & &\\
	\hline
	\multicolumn{4}{|c|}{\emph{State Estimation}} \\
	\hline
	$\chi$ & Matrix of sigma vectors & &\\
	$\lambda$& Scaling parameter & &\\
	$\alpha$& Determines the spread of sigma points & &\\
	$\beta$& Prior knowledge of the sigma points distribution & &\\
	$\kappa$& Scaling parameter & & \\
	$W$& Sigma vecors weights & & \\
   	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate & & \\
   	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate & & \\
   	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate & & \\
   	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate & & \\
   	$P^f_t$ & Forward posterior covariance matrix & & \\
   	$P^{f-}_t$ & Forward prior covariance matrix & & \\
   	$P^b_t$ & Backward posterior covariance matrix & & \\
   	$P^{b-}_t$ & Backward prior covariance matrix & & \\
	$\mathcal K_{t} $& Filter gain & & \\
	$M_t$& Cross-covariance matrix & & \\
	$S_t$& Smoother gain & & \\	
	\hline
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

% ~~~~~~~~~~~~~~~~~~~~

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	$\chi$ & Matrix of sigma vectors \\
	$\lambda$& Scaling parameter\\
	$\alpha$& Determines the spread of sigma points\\
	$\beta$& Prior knowledge of the sigma points distribution\\
	$\kappa$& Scaling parameter\\
	$W$& Sigma vecors weights\\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix \\
    	$P^b_t$ & Backward posterior covariance matrix \\
    	$P^{b-}_t$ & Backward prior covariance matrix \\
	$\mathcal K_{t} $& Filter gain\\
	$M_t$& Cross-covariance matrix\\
	$S_t$& Smoother gain
    \end{tabular}
    \caption{State Estimation}
\end{table}

% ~~~~~~~~~~~~~~~~~~~
\begin{table}[!ht]
\caption{
\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
\begin{tabular}{|c|}\hline
\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\\ \hline
\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
\\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
\\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\\
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
\\
$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
\\
$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
\\\hline
\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
\\\hline
\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
\\
$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
\\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
\\
$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
\\
\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
\\
$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
\\
$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
\\
$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\\hline
\end{tabular}
\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm. The steps are iterated 11 times for our state estimation procedure. The least squares algorithm is run after each iteration to update the parameter estimates.
\end{flushleft}
\label{tab:UKFAlgorithm}
\end{table}

>>>>

\begin{table}[!ht]
\caption{
\bf{Notation and Parameters - Part 2}}
\begin{tabular}{|c|l|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
	\hline
	$\hat{\mathbf{x}}$ & State estimate & & \\
    $L$ & number of field basis functions & 81 & \\
   	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
   	$\mathbf{x}_t$ & state vector at time $t$ & & \\
   	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
   	$\theta$ & vector of connectivity kernel parameters & & \\
   	$\Gamma$ & inner product of field basis functions & &\\
   	$q()$ & state function & &\\
   	$Q()$ & state function & &\\
	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
   	$\mathbf{e}_t$ & state disturbance & &\\
	$\Sigma_e$ &state disturbance covariance matrix& &\\
	$\mathbf{\varepsilon}_t$ & observation noise & &\\
	$\Sigma_{\varepsilon}$ &observation noise covariance matrix& &\\
   	$\mathbf{C}$ & observation matrix& & \\
	$c_{ij}$& elements of observation matrix & & \\
	\hline
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}} \\
	\hline
    $V(\nu)$ & Spectrum of the dynamic field & &\\
	$\nu$ & Spatial frequency & &\\
	$\nu_c$ & Spatial cut-off frequency & &\\
	$\Delta_y$ & Distance between adjacent sensors & &\\
	$\rho$ & Over-sampling parameter & &\\
	$\Delta_{\phi}$ & Distance between field basis functions & &\\
	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function & &\\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & &\\
	\hline
	\multicolumn{4}{|c|}{\emph{State Estimation}} \\
	\hline
	$\chi$ & Matrix of sigma vectors & &\\
	$\lambda$& Scaling parameter & &\\
	$\alpha$& Determines the spread of sigma points & &\\
	$\beta$& Prior knowledge of the sigma points distribution & &\\
	$\kappa$& Scaling parameter & & \\
	$W$& Sigma vecors weights & & \\
   	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate & & \\
   	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate & & \\
   	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate & & \\
   	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate & & \\
   	$P^f_t$ & Forward posterior covariance matrix & & \\
   	$P^{f-}_t$ & Forward prior covariance matrix & & \\
   	$P^b_t$ & Backward posterior covariance matrix & & \\
   	$P^{b-}_t$ & Backward prior covariance matrix & & \\
	$\mathcal K_{t} $& Filter gain & & \\
	$M_t$& Cross-covariance matrix & & \\
	$S_t$& Smoother gain & & \\	
	\hline
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

\begin{table}[!ht]
\caption{
\bf{Steps in the Algorithm for the Unscented RTS Smoother}}
\begin{tabular}{|c|}\hline
\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialisation} \\ 
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\\ \hline
\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix} \\
\\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
\\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\\
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
\\
$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
\\
$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
\\\hline
\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialisation}\\
$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
\\\hline
\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t \in \left\lbrace T-1, \cdots, 0 \right\rbrace $ calculate the sigma points $\mathcal X_{i,t}^b$ and propagate them through equation \ref{eq:QmatrixForSigmapoints}}\\
$\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L$\\
\\
\multicolumn{1}{|p{16cm}|}{Calculate the predicted state and the predicted covariance matrix}\\
\\
$\hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}$\\
\\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e $\\
\\
$\mathbf M_{t +1}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t}^{b-}-\hat{\mathbf x}_{t}^{f})(\mathcal X_{i,t+1}^{b-}-\hat{\mathbf x}_{t+1}^{b-})^\top$\\
\\
\multicolumn{1}{|p{16cm}|}{Compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\
\\
$\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1} $\\
\\
$\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right]$\\
\\
$\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top $\\\hline
\end{tabular}
\begin{flushleft}This table shows the steps in the unscented Rauch-Tung-Striebel smoother algorithm. The steps are iterated 11 times for our state estimation procedure. The least squares algorithm is run after each iteration to update the parameter estimates.
\end{flushleft}
\label{tab:UKFAlgorithm}
\end{table}
